VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-03 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
newest article

\begin{proof}
Note that 
\begin{equation}
\label{eq:diff}
\frac{dg_t^{\alpha}(\tau)}{d\tau} = \frac{\alpha(t-\tau)^{\alpha-1}}{\Gamma(\alpha+1)} =\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}. 
\end{equation}
Furthermore,
\begin{equation}
\label{eq:inter_step}
\int_{a'}^{t} f(\tau)\,dg_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau) \frac{dg_t^{\alpha}(\tau)}{d\tau}\,dg_t^{\alpha}(\tau). 
\end{equation}
The desired result is obtained by substituting Equation~\eqref{eq:diff} into Equation~\eqref{eq:inter_step}.  
\end{proof}

In this section we present a novel geometric interpretation of the Riemann-Liouville fractional integral. 
Recall that the Riemann-Liouville fractional integral of order $\alpha$ is defined as:
\begin{equation}
\label{eq:RL_frac_int}
\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
\end{equation}

\noindent
Podlubny showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
\begin{equation}
\label{eq:rs}
\int_0^{t} f(\tau)~dg_t(\tau),
\end{equation}
with 
\begin{equation}
\label{eq:g_rl}
g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
\end{equation}

\noindent
Note that $g_t^{\alpha}(\tau)$ is always invertible, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$. The inverse 
of $g_t^{\alpha}(\tau)$ is equal to:
\begin{equation}
h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}
\end{equation}

@@

\begin{table}[h!]
 \centering
 \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.}
 \label{tab:gandh}
 \begin{tabular}{|c || c | c|} 
 \hline
 $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
 \hline\hline
 $0$ & 0 & $y=0$ \\ 
 $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
 $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
 $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
 $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex] 
 $1$ & $\tau$ & $\tau$ \\ [1ex] 
 \hline
 \end{tabular}
 \end{table}

>>>>

\begin{proof}
Note that 
\begin{equation}
\label{eq:diff}
\frac{dg_t^{\alpha}(\tau)}{d\tau} = \frac{\alpha(t-\tau)^{\alpha-1}}{\Gamma(\alpha+1)} =\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}. 
\end{equation}
Furthermore,
\begin{equation}
\label{eq:inter_step}
\int_{a'}^{t} f(\tau)\,dg_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau) \frac{dg_t^{\alpha}(\tau)}{d\tau}\,d\tau. 
\end{equation}
The desired result is obtained by substituting Equation~\eqref{eq:diff} into Equation~\eqref{eq:inter_step}.  
\end{proof}

\begin{theorem}
If $\tau\in(-\infty,t]$ then $g_t^{\alpha}(\tau)$ is an invertable function. Its inverse is:
\begin{equation}
h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
\end{equation}
\end{theorem}
\begin{proof}
The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ if $\tau\in(-\infty,t]$. The inverse now follows trivially.  
\end{proof}

@@

\begin{table}[h!]
 \centering
 \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The expressions in this table are depicted in Fig~\ref{fig:gandh}.}
 \label{tab:gandh}
 \begin{tabular}{|c || c | c|} 
 \hline
 $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
 \hline\hline
 $0$ & 0 & $y=0$ \\ 
 $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
 $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10^2} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
 $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10^3} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
 $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10^4} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex] 
 $1$ & $\tau$ & $\tau$ \\ [1ex] 
 \hline
 \end{tabular}
 \end{table}
